---
title: "R Notebook"
output: html_notebook
---


```{r}
library(dplyr)
library(lubridate)
library(zoo)
library(readr)
```

```{r}
df <- read_csv("./data/btc/df-out.csv", sep = '\t')
df_raw <- read_csv("./data/btc/coinbaseUSD.csv")

df$DateTime_UTC <- df$DateTime_UTC %>% as.POSIXct()
df %>% head
```

```{r}
d2 <- df
```

```{r}
df <- d2

df <- df %>% select(-X, -close_price_returns_bins, -DateTime_UTCIs_month_end, -DateTime_UTCIs_month_start, -DateTime_UTCIs_quarter_end, -DateTime_UTCIs_quarter_start, -DateTime_UTCIs_year_end, -DateTime_UTCIs_year_start, -close_price_returns_y)

df <- df %>% 
  rename(date = DateTime_UTC,
         close_price_returns = close_price_returns_x,
         year = DateTime_UTCYear,
         month = DateTime_UTCMonth,
         week = DateTime_UTCWeek,
         day = DateTime_UTCDay,
         dayofweek = DateTime_UTCDayofweek,
         dayofyear = DateTime_UTCDayofyear)

y <- df$price_close

y <- y[2:length(y)]
df <- df[1:nrow(df)-1, ]

df <- cbind(data.frame(y=y), df)

```

#### More Featurue engineering maybe
rolling quantils thing for:
  - sum(volume)
  - sum(volume) / max(last7 volumes)
  - return labels
  - sequential down/up
  - return (like a moving average)

Might also be good to have number of ticks per time period (number of trades happening, not just overall volume). Need to go back to the data generator for that one.

Also want to get high and low incorporated in there somehow...
  - high's % over close
  - low's % under close
  
Also need more time features:
  - Hour, Minute, and Second
  
  
```{r}
d <- df %>%
  mutate(hour = hour(date)) %>%
  mutate(minute = minute(date)) %>% 
  mutate(up = if_else(lag(price_close) < price_close, 1, 0)) %>%
  mutate(down = if_else(lag(price_close) > price_close, 1, 0)) %>%
  mutate(up = if_else(is.na(up), 0, up)) %>%
  mutate(down = if_else(is.na(down), 1, down)) %>%
  mutate(per_high = (price_high - price_close)/price_close) %>%
  mutate(per_low = (price_close - price_low)/price_close) %>%
  # mutate(per_vol = volume*price_close/price_close) %>%
  # rolling 3
  mutate(rolling_3_volume = rollapply(volume, 3, mean, align = 'right', fill=volume)) %>%
  mutate(rolling_3_volume_over_max = rollapply(volume, 3, sum, align = 'right', fill=volume)) %>%
  mutate(rolling_3_volume_over_max = rolling_3_volume_over_max / max(1e-7, rollapply(volume, 7, # using 7 to be interesting
                                                                           max, align = 'right', fill=rolling_3_volume))) %>%
  mutate(rolling_3_return = rollapply(close_price_returns, 3, mean, align = 'right', fill=close_price_returns)) %>%
  mutate(rolling_3_return_labels = rollapply(close_price_returns_labels, 3, mean, align = 'right', fill=close_price_returns_labels)) %>%
  mutate(rolling_3_seq_down = rollapply(down, 3, sum, align = 'right', fill=0)) %>%
  mutate(rolling_3_seq_up = rollapply(up, 3, sum, align = 'right', fill=0)) %>%
  #rolling 7
  mutate(rolling_7_volume = rollapply(volume, 7, mean, align = 'right', fill=volume)) %>%
  mutate(rolling_7_volume_over_max = rollapply(volume, 7, sum, align = 'right', fill=volume)) %>%
  mutate(rolling_7_volume_over_max = rolling_7_volume_over_max / max(1e-7, rollapply(volume, 7, max, align = 'right', fill=rolling_7_volume))) %>%
  mutate(rolling_7_return = rollapply(close_price_returns, 7, mean, align = 'right', fill=close_price_returns)) %>%
  mutate(rolling_7_return_labels = rollapply(close_price_returns_labels, 7, mean, align = 'right', fill=close_price_returns_labels)) %>%
  mutate(rolling_7_seq_down = rollapply(down, 7, sum, align = 'right', fill=0)) %>%
  mutate(rolling_7_seq_up = rollapply(up, 7, sum, align = 'right', fill=0)) %>%
  # rolling 10
  mutate(rolling_10_volume = rollapply(volume, 10, mean, align = 'right', fill=volume)) %>%
  mutate(rolling_10_volume_over_max = rollapply(volume, 10, sum, align = 'right', fill=volume)) %>%
  mutate(rolling_10_volume_over_max = rolling_10_volume_over_max / max(1e-7, rollapply(volume, 10, max, align = 'right', fill=rolling_10_volume))) %>%
  mutate(rolling_10_return = rollapply(close_price_returns, 10, mean, align = 'right', fill=close_price_returns)) %>%
  mutate(rolling_10_return_labels = rollapply(close_price_returns_labels, 10, mean, align = 'right', fill=close_price_returns_labels)) %>%
  mutate(rolling_10_seq_down = rollapply(down, 10, sum, align = 'right', fill=0)) %>%
  mutate(rolling_10_seq_up = rollapply(up, 10, sum, align = 'right', fill=0)) %>%
  # rolling 20
  mutate(rolling_20_volume = rollapply(volume, 20, mean, align = 'right', fill=volume)) %>%
  mutate(rolling_20_volume_over_max = rollapply(volume, 20, sum, align = 'right', fill=volume)) %>%
  mutate(rolling_20_volume_over_max = rolling_20_volume_over_max / max(1e-7, rollapply(volume, 20, max, align = 'right', fill=rolling_20_volume))) %>%
  mutate(rolling_20_return = rollapply(close_price_returns, 20, mean, align = 'right', fill=close_price_returns)) %>%
  mutate(rolling_20_return_labels = rollapply(close_price_returns_labels, 20, mean, align = 'right', fill=close_price_returns_labels)) %>%
  mutate(rolling_20_seq_down = rollapply(down, 20, sum, align = 'right', fill=0)) %>%
  mutate(rolling_20_seq_up = rollapply(up, 20, sum, align = 'right', fill=0)) %>%

  mutate(UP = if_else(close_price_returns > 1e-4, 1, 0)) %>%
  mutate(DOWN = if_else(close_price_returns < -1*1e-4, 1, 0)) %>%
  mutate(HOLD = if_else(UP == DOWN, 1, 0))
  
d %>%
  # select(date, y, price_close, close_price_returns, up, down) %>%
  # select(date, y, price_close, close_price_returns, up, down, UP, DOWN, HOLD) %>%
  # select(date, y, price_close, volume,
  #        rolling_3_volume, rolling_3_volume_over_max, rolling_3_return, 
  #        rolling_3_return_labels, rolling_3_seq_down, rolling_3_seq_up) %>%
  # filter(date > '2015-01-27') %>% # this seems to be the start of real trading 
  summary
  
names(d)

```

```{r}
write.csv(d, "./data/btc/btc-final.csv", sep = "\t")
```

































