---
title: "scrape 5min data"
subtitle: "Using R to Access Cryptocurrency Exchange APIs"
author: "Liam Corrigan"
date: "March 20, 2018"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: true
    number_sections: false
    theme: cerulean
    highlight: zenburn
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```



# Background

# Libraries
The special libraries used for this project are:
```{r message=FALSE, warning=FALSE}
# install.packages("httr")
# install.packages("Rbitcoin")
# install.packages("PoloniexR")
library(httr)
library(Rbitcoin)
library(PoloniexR)
```
Install these if you don't already have them. You'll also need the following packages:
```{r message=FALSE, warning=FALSE}
library(quantmod)
library(magrittr)
library(plyr)
library(dplyr)
library(scales)
library(ggplot2)
```

# Step 1: Poloniex Data
Poloniex is the exchange where I do all my person crypto-to-crypto trading. At the time of this post Poloniex offers 69 different coins that can be traded against bitcoin.

They offer an API so traders can access exchange data for things like building trading bots, or writing posts like this! [Check out the API here.](https://poloniex.com/support/api/)

## Using PoloniexR
We could use hhtr to access this API but instread we are going to test out a cool package made by VermeirJellen called PoloniexR [(check out the github here)](https://github.com/VermeirJellen/PoloniexR).

First, set up the public API.
```{r}
poloniex_public <- PoloniexPublicAPI()
```
## Ticker Data
Next, lets get a list of all the coins traded on Poloniex.
```{r}
ticker_info     <- ReturnTicker(poloniex_public)
head(ticker_info)
```
This returns a `data.frame` where each row represents a currency pair that can be traded. Unfortunately it uses rownames as the names to dictate each currency pair, and rownames do not play well with my favourite package `dplyr`, so lets convert these rownames into a column of their own.

```{r}
ticker_info <- cbind(pairs = rownames(ticker_info), ticker_info)
rownames(ticker_info) <- NULL
ticker_info$pairs %<>% as.character()
colnames(ticker_info)
head(ticker_info)
```

## Chart Data
Next, lets get some chart data. We will first look at getting data for the USDT_BTC pair. We will collect data back to the start of 2015 based on one day trading periods.

### Get Sample Chart Data for BTC_ETH
*_This code was copied from the PoloniexR github tutorial._
```{r}
# ?ReturnChartData
Sys.setenv(tz="UTC")
pair    <- "USDT_BTC"
from    <- as.POSIXct("2017-01-01 00:00:00 UTC")
to      <- as.POSIXct("2018-03-28 00:00:00 UTC")
period  <- "5M" #"D" #"5M", "15M", "30M", "2H", "4H", "D"

chart.data <- ReturnChartData(theObject = poloniex_public,
                              pair      = pair,
                              from      = from,
                              to        = to,
                              period    = period)
head(chart.data)
```
The chart data is returned in an `xts` object which is essentially a `zoo` object. This type of object is special for handling time series data in R. 

```{r}
chart_data <- chart.data %>% as.data.frame()
chart_data <- chart_data %>%
  select(
    price_open = open,
    price_high = high,
    price_low = low,
    price_close = close
  )

write.csv(chart_data, "./data/btc/btc_poloniex/2017-01-01_2018-03-28.csv")

```






